Followers Are Not Enough: A Question-Oriented\alert{Multi-faceted} Approach to Community Detection in Online Social Networks

### 2014-11-18 paper-postreview/results.tex
Addressed next actions.
Addressed my next actions from

action-items-141114.txt

Each community type (Structural, Activity-based, Topic-based, Interaction-based) induces a different partition of the edges, and each edge type (Transfer Entropy, Hashtag, Mention-Retweet) induces a different distribution of weights. That is, let $W_{u \to f}$ be the weight on an edge $E_{u \to f}$ chosen uniformly at random from the network, and compute
\begin{align}
	P(W_{u \to f} \leq w_{u \to f} | T(E_{u \to f}) = t),
\end{align}
the empirical distribution over the edge weights conditioned on the edge type $t$ being one of inter, intra, and mixed. For meaningful community structure, we expect the distribution of edge weights to differ with the edge type $t$. If the community structure were arbitrary, the edge weights would be independent of the edge type, and all three conditional distributions would be identical.
The densities associated with these distributions are shown in Figure~\ref{Fig-distributions_by_types}.
\begin{figure}[!h]
	\centering
	\includegraphics[width=1\textwidth]{densities-edges}
	\caption{The density of edge weights for different community types (rows) and weight types (columns). The red,  blue, and purple values below each collection of densities indicate the median of weight on intra-, inter-, and mixed-edges, respectively.}
	\label{Fig-distributions_by_types}
\end{figure}

>>>>

Each community type (Structural, Activity-based, Topic-based, Interaction-based) induces a different partition of the edges, and each edge type (Transfer Entropy, Hashtag, Mention-Retweet) induces a different distribution of weights. That is, let $W_{u \to f}$ be the weight on an edge $E_{u \to f}$ chosen uniformly at random from the network, and compute
\begin{align}
	P(W_{u \to f} \leq w_{u \to f} | T(E_{u \to f}) = t),
\end{align}
the empirical distribution over the edge weights conditioned on the edge type $t$ being one of inter, intra, and mixed. The densities associated with these distributions are shown in Figure~\ref{Fig-distributions_by_types}. By considering how the weights vary conditional on the edge type, we can explore whether and how each of the follower-, interaction-, activity-, and topic-based communities define functional units within the network. For example, if users interact more-or-less independently of the topics they discuss, then the distributions of the interaction-based / topic-based edge weights should be independent of the edge type determined from the topic-based / interaction-based communities. By contrast, if users tend to interact mostly with those users who discuss similar topics, then the edge weight distributions should vary with the edge type.
%For meaningful community structure, we expect the distribution of edge weights to differ with the edge type $t$. If the community structure were arbitrary, the edge weights would be independent of the edge type, and all three conditional distributions would be identical.
\begin{figure}[!h]
	\centering
	\includegraphics[width=1\textwidth]{densities-edges}
	\caption{The density of edge weights for different community types (rows) and weight types (columns). The red,  blue, and purple values below each collection of densities indicate the median of weight on intra-, inter-, and mixed-edges, respectively.}
	\label{Fig-distributions_by_types}
\end{figure}
